\documentclass[letterpaper]{article}

\usepackage{ulem}
\usepackage{contour}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.25in]{geometry}

\hypersetup{
  colorlinks = true,
  urlcolor   = RoyalBlue!75!white,
}

\raggedright
\raggedbottom
\urlstyle{same}
\setlength{\tabcolsep}{0in}
\AtBeginDocument{\normalem}

\newlength{\uppercaseHeight}
\AtBeginDocument{\settoheight{\uppercaseHeight}{A}}

% Ensure output is parsable
\pdfgentounicode=1
\input{glyphtounicode}

% Sections formatting
\titleformat{\section}{\vspace{-9pt}\scshape\raggedright\large}{}{0em}{}[\color{gray}\titlerule\vspace{-7pt}]

% Beautiful underline
\renewcommand{\ULdepth}{2pt}
\contourlength{1pt}

\newcommand{\beauline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\[-0.075em]
    \end{tabular*} \\[-0.05em]
}

\newcommand{\resumeHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*} \vspace{-3pt}
}

\newcommand{\resumeSmallHeading}[1]{
    \item {\small#1 \vspace{-0.75em}}
}

\newcommand\badgeStrut{\rule[-1pt]{0pt}{\uppercaseHeight}}
\newtcbox{\badge}{
  on line,
  enhanced,
  arc=3pt,
  top=2pt,
  left=5pt,
  right=5pt,
  bottom=2pt,
  boxsep=0pt,
  boxrule=0.25pt,
  colback=white!95!gray,
  enlarge bottom by=2pt,
  fontupper=\scriptsize\badgeStrut\color{black},
}
\newcommand{\badges}[1]{
  \foreach \b in #1 {
    \badge{\b}\hspace{-3pt}
  }
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.125in, label={}]}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-4pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\link}[2]{\href{#1}{\beauline{#2}}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

% ------------------------------------------------------------ %

\begin{center}
	\textbf{\Huge Oganes Mirzoyan} \\[0.5em]
	\link{mailto:mirzoyan.oganes@mail.ru}{mirzoyan.oganes@mail.ru} ~
	\link{https://github.com/senago}{github.com/senago} ~
	\link{https://gitlab.com/senago}{gitlab.com/senago} ~
	\link{https://t.me/senago}{t.me/senago}
\end{center}

% ------------------------------------------------------------ %

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Bauman Moscow State Technical University}{Sep. 2020 - May 2026}
{Specialist of Computer Security}{Moscow, Russia}

\resumeSubheading
{Yandex School of Data Analysis}{Sep. 2022 - May 2024}
{Big Data Infrastructure}{Moscow, Russia}
\badges{{Rust, C++, Assembly, Algorithms and Data Structures, Computer Architecture and Operating Systems}}

\resumeSubheading
{VK Technology Park}{Sep. 2021 - May 2022}
{Systems Architect}{Moscow, Russia}
\badges{{C, C++, Algorithms and Data Structures, Computer Networks, Concurrency, Distributed Systems}}\\
\badges{{Databases, Go, Frontend Development, Communication Skills, UX/UI}}

\resumeSubHeadingListEnd

% ------------------------------------------------------------ %

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Ozon Fintech}{July 2022 -- Present}
{Junior Software Engineer $|$ Core Banking System}{Moscow, Russia}
\badges{{Finance, Billing, Go, Microservices, Kubernetes, Kafka, PostgreSQL, SRE}}

\resumeSubheading
{ProCSy JSC}{July 2021 -- Sep. 2021}
{Software Engineering Intern $|$ Distributed Document-Oriented Service}{Moscow, Russia}
\badges{{Go, Cryptography, Document Parsing and Generation, Hyperledger Fabric}}
\resumeItemListStart
\resumeItem{Worked in a team of 3 developers to implement the API for a power of attorney management service.}
\resumeItem{Learned new technologies and patterns for documenting and testing the code.}
\resumeItem{Improved soft skills communicating with the frontend development team and the project manager.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ------------------------------------------------------------ %

\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Social Network}{Feb. 2022 -- May. 2022}
{Coursework}{Moscow, Russia}
\badges{{Go, Microservices, TypeScript, UX/UI, Responsive Design}}
\resumeItemListStart
\resumeItem{Implemented API for a social network service.}
\resumeItem{Built a React-like framework \link{https://github.com/senago/treact}{github.com/senago/treact} in TypeScript from scratch with jsx and hooks.}
\resumeItem{Designed and implemented a responsive website.}
\resumeItemListEnd

\resumeSubheading
{Distributed Fault-Tolerance Computing}{Sep. 2021 -- Dec. 2021}
{Coursework $|$ \link{https://gitlab.com/senago/abeille}{gitlab.com/senago/abeille}}{Moscow, Russia}
\badges{{C, C++, Raft, gRPC, Concurrency, Distributed Systems, IPC}}
\resumeItemListStart
\resumeItem{Implemented Raft for consensus over the tasks for worker nodes.}
\resumeItem{Implemented client and server sides for users and workers (including IPC for worker nodes).}
\resumeItem{Got acquainted with the RPC protocol (and, specifically, with gRPC).}
\resumeItemListEnd

\resumeSubheading
{Restock Monitor}{Sep. 2017 -- Aug. 2018}
{School Project}{Moscow, Russia}
\badges{{Go, REST, Web Scraping, Concurrency, Headless Browsers, UX/UI}}
\resumeItemListStart
\resumeItem{Developed a multitask web scrapper for more than 100 websites.}
\resumeItem{Got used to headless browsers (such as \emph{chromedp}).}
\resumeItem{Developed a sophisticated web application for controlling the restock monitor.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ------------------------------------------------------------ %

\section{Accomplishments}
\resumeSubHeadingListStart

\resumeHeading
{Third place in the \textbf{Web3Souls} Hackathon (Web Service for Providing Smart Contracts Audits)}{Dec. 2022}

\resumeHeading
{Top 10\% (5/61) in the \textbf{Sovcombank Team Challenge 2022} Hackathon (Web Service for Currency Trading)}{Nov. 2022}

\resumeHeading
{Silver Medal at \textbf{IMC 2022}}{Aug. 2022}

\resumeHeading
{Second Place in the \textbf{Junction} Hackathon (Hybrid Event Experience Gamefied Challenge by Brella)}{Nov. 2021}

\resumeHeading
{Diploma in the Round 2 among University Students of \textbf{NSUCRYPTO} (International Olympiad in Cryptography)}{Oct. 2021}

\resumeHeading
{Bronze Medal at \textbf{IMC 2021}}{Aug. 2021}

\resumeSubHeadingListEnd

% ------------------------------------------------------------ %

\section{Skills}
\resumeSubHeadingListStart

\resumeSmallHeading
{\textbf{Programming Languages}:\badges{{Go, C, C++, Rust, JavaScript/TypeScript, Python, Bash}}}

\resumeSmallHeading
{\textbf{Databases}:\badges{{PostgreSQL, MongoDB, ClickHouse, Redis}}}

\resumeSmallHeading
{\textbf{Technologies}:\badges{{Kafka, gRPC, Protobuf, Docker, Kubernetes, React, Django, Svelte}}}

\resumeSmallHeading
{\textbf{Misc.}:\badges{{Linux, SQL, GraphQL, HTML/CSS, Nginx, Prometheus, Grafana, Swagger, Figma}}}

\resumeSmallHeading
{\textbf{Spoken Languages}:\badges{{Russian (native speaker), English (fluent)}}}

\resumeSubHeadingListEnd

\section{Interests}
\resumeSubHeadingListStart

\resumeSmallHeading{\badges{{Backend Development, Highload and Distributed Systems, Site Reliability Engineering}}}

\resumeSmallHeading{\badges{{Homomorphic Encryption, Abstract Algebra, Cryptography}}}

\resumeSubHeadingListEnd

\end{document}
